---
title: "Working Hours"
author: "Mark van der Sman"
date: "14 december 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)
library(corrgram)
theme_set(theme_bw())
```

```{r data, echo=FALSE}
data <- as.data.frame(read.csv("WorkingHours.csv"))
data$Room <- as.factor(data$Room)
data <- data %>% group_by(Room, Cleaning.type) %>% mutate(Mean_room=mean(Minutes), Mean_SD=sd(Minutes)) %>% group_by(Cleaning.type) %>% mutate(Mean_Type=mean(Minutes)) %>% arrange(Distance)
```

The used dataset is acquired from [this Reddit post](https://www.reddit.com/r/DataVizRequests/comments/7jqso6/request_i_would_like_to_have_some_simple_graphs/) on DataViz Requests. For more information on the data, please read the post.

## Exploring the data

First some simple boxplots and scatterplots to get a general overview.

```{r explore1, echo=FALSE}
ggplot(data, aes(x=Room, y=Minutes)) +
  geom_boxplot() +
  facet_wrap(~Cleaning.type) +
  ggtitle("Time taken to clean a room","Facetted by the type of clean-up")
```

> This plot shows a clear difference between the time needed to clean a room upon checkout compared to the time needed for a stay-over.

```{r explore2, echo=FALSE}
ggplot(data, aes(x=Cleaning.type, y=Minutes)) +
  geom_boxplot() +
  ggtitle("Time taken for both types of clean-up")
```

> The previous claim is supported by this plot, showing a clear difference between the two means of the types of cleaning.

```{r explore3, echo=FALSE}
ggplot(data, aes(x=Distance, y=Minutes, group=Cleaning.type, shape=Cleaning.type)) +
  geom_jitter() +
  geom_line(aes(y=Mean_room, linetype=Cleaning.type)) +
  scale_shape_manual(values=c(3,1)) +
  ggtitle("Time taken to clean a room","Grouped by the type of clean-up")
```

> The same conclusions can be drawn from this jitterplot

```{r explore4, echo=FALSE}
ggplot(data, aes(x=Distance, y=Minutes, group=Cleaning.type)) +
  geom_line(aes(y=Mean_room, linetype=Cleaning.type)) +
  geom_errorbar(aes(ymin=Mean_room-Mean_SD, ymax=Mean_room+Mean_SD)) +
  ggtitle("Time taken to clean a room","Grouped by the type of clean-up")
```

> Because of the density of some ranges, the errorbars (&#177;1SD) were chosen for a cleaner plot. This suggests a clear difference between the two cleaning types. The distance does not, however, show any significant differences in the time measured other than an increase in variance for the longer distances.

## Correlation?

Let's see if the correlation between Distance, Cleaning.type and Minutes is large enough.

```{r corrgram, echo=FALSE}
corrgram(data, order=FALSE, lower.panel=panel.conf, upper.panel=panel.pts,
         diag.panel=panel.density, main="Correlation matrix")
```

> The correlation table shows that the average cleaning time per room per type (Mean_room) is highly correlated with the average cleaning time per type (Mean_Type), indicating that the distance does not influence the cleaning time for a certain type. The low correlation of Distance with Minutes shows no relation between these two variables: the cleaning time is not influenced by the distance of a room.
